Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-07 paper.qmd
Updated error computation of Figure 6

error_df_two_curvy_abs <- error_df_two_curvy_abs |>
  mutate(sqrt_row_wise_abs_error = sqrt(row_wise_abs_error))

@@

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  theme(
    aspect.ratio = 1
  )

error_plot_two_curvy_hist <- 
  ggplot(error_df_two_curvy_abs) +
  geom_histogram(aes(x=sqrt_row_wise_abs_error, y=..density..)) +
  geom_density(aes(x=sqrt_row_wise_abs_error, y=..density..), colour="red") +
  xlab(expression(group("|", e[hj], "|"))) +
  ylab("") +
  theme_bw() 
```

```{r}
#| label: fig-p-d-error-in-2d-two-curvy
#| fig-cap: "The $7\\text{-}D$ model error in \\gD{} layout. Color indicates square root of absolute error, dark blue indicating high error and light indicates low error. Most large errors are distributed near the edges of the clusters."
#| out-width: 60%
#| fig-pos: H

>>>>

error_df_two_curvy_abs <- error_df_two_curvy_abs |>
  mutate(sqrt_row_wise_total_error = sqrt(row_wise_total_error))

@@

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_total_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  theme(
    aspect.ratio = 1
  )

error_plot_two_curvy_hist <- 
  ggplot(error_df_two_curvy_abs) +
  geom_histogram(aes(x=sqrt_row_wise_total_error, y=..density..)) +
  geom_density(aes(x=sqrt_row_wise_total_error, y=..density..), colour="red") +
  xlab(expression(group("|", e[hj], "|"))) +
  ylab("") +
  theme_bw() 
```

```{r}
#| label: fig-p-d-error-in-2d-two-curvy
#| fig-cap: "The $7\\text{-}D$ model error in \\gD{} layout. Color indicates square root of total error, dark blue indicating high error and light indicates low error. Most large errors are distributed near the edges of the clusters."
#| out-width: 60%
#| fig-pos: H
